\documentclass[margin,line]{res}
\usepackage{enumerate}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\setlength{\parskip}{0cm}
\setlength{\parindent}{.3cm}


\begin{document}
\name{Christopher F. Bradish}
\begin{resume}
\section{\sc Contact Information}
\begin{tabbing}
\hspace{1.3in}\=\hspace{1.3in}\=\hspace{1.3in}\=\hspace{1.3in}\kill
\>\>\textbf{E-mail:}\>chris@bradi.sh\\             
\end{tabbing}


\section{\sc Education}
\vspace{-.128in}
\begin{tabbing}
\hspace{2.3in}\=\hspace{2.3in}\kill
\textbf{1969-1972}\>Hertford College, Oxford\\
1972\>B.A. (Physics)\\
1977\>M.A.\\
\\
\textbf{1972-1977}\>King's College Hospital, London\\
1977\>M.B. B.S.\\
\\
\textbf{1977}\>M.R.C.S., L.R.C.P.\\
\textbf{1981}\>F.R.C.S (Eng)\\
\end{tabbing}

\section{\sc Prizes and Awards}
\vspace{-.128in}
\begin{tabbing}
\hspace{2.3in}\=\hspace{2.3in}\kill
\textbf{1977}\>Jelf Medal \& Legg Prize\\
\textbf{1986}\>AO Travelling Fellowship\\
\textbf{1987}\>British Orthopaedic Assosciation Travelling Fellowship\\
\end{tabbing}

\section{\sc Professional Experience}
\noindent{}I was appointed Consultant in Orthopaedics in 1988, working at the Birmingham Children's Hospital and the Royal Orthopaedic Hospital, Birmingham. I  moved  to  London  in  2008  on appointment to  Great  Ormond  Street Hospital, where  I was the Senior Orthopaedic  Surgeon. My practice  covered  all aspects  of children's orthopaedics with the exception of spinal surgery.\\
\\
I retired from NHS practice at the end of 2014.\\
\\
I have subsequently continued to undertake medicolegal work in relation to children's orthopaedics.\\
\\
I remain an Honorary Consultant at Great Ormond Street Hospital. 

\section{\sc Memberships \\ and \\ Duties within Learned \\ Societies}
\vspace{-0.2in}
\noindent{}\subsubsection{Current}
\begin{enumerate}
\item British Orthopaedic Association
\item British Society for Children's Orthopaedic Surgery
\item British Limb Reconstruction Society 
\end{enumerate}
\subsubsection{Previous}
\begin{enumerate}
\item British Orthopaedic Association\\
Member of Council 2002-2005\\
Member of following committees:
\begin{enumerate}
\item Medicolegal committee
\item CPD committee
\end{enumerate}
\item British Society for Children's Orthopaedic Surgery\\
President 2008-2010
\item British Orthopaedic Foot and Ankle Society
\item Skeletal Dysplasia Group.
\item British Limb Reconstruction Society:\\
Secretary 1994 - 1998\\
President 1998 - 2000
\item European Paediatric Orthopaedic Society
\item Clinical Reviewer for Royal College of Surgeons of England 2005-2008
\item President of Naughton Dunn Club 2006
\item Examiner for FRCS (Tr and Orth) 2000-2005
\end{enumerate}

\section{\sc Paediatric Publications}
\begin{enumerate}
\item Davidson T.I., Bradish C.F.\\
Angiosarcoma arising in a patient with Maffuci syndrome.\\
European Journal of Surgical Oncology1985; 11: 381-384.
\item Bradish C.F., Flowers M.\\
Central retinal artery occlusion in association with osteogenesis imperfecta.\\
Spine 1987; 12: 193-194.
\item Bradish C.F., Davis S.\\
Tibia vara due to fibrocartilaginous  dysplasia - the natural history.\\
Journal of Bone and Joint Surgery (Br) 1988; 70B: 106-108.
\item Bradish C.F., Marshall J.H.\\
Callotasis in Melorheostosis: a case report.\\
Journal of Bone and Joint Surgery (Br) 1993; 75B: 155.
\item Bradish C.F., Gibbons P.\\
Fibular Hemimelia, the management of the severe deformity.\\
Journal of Paediatric Orthopaedics 3: 1996.
\item Bradish C.F.,\\
Die Behandlung der fibularen Hemimelie.  (Invited paper on fibular hemimelia).\\
Orthopaede 1999; 28:1034-1044
\item Bryan R., Bradish C.F.,\\
Primary sternal osteomyelitis in infants: a presentation of two cases.\\
Journal of Paediatric Orthopaedics (B) 1999.
\item Bradish C.F., Noor S.\\
The Ilizarov method in the management of relapsed club feet.\\
Journal of Bone and Joint Surgery (Br) 2000.
\item Bradish C.F., Tan K\\
Bone cysts following the Ilizarov correction of foot deformities.\\
Journal of Paediatric Orthopaedics.
\item Bradish C.F., Bache C.E., Myers G. and Gibbons P.\\
Leg lengthening in bone dysplasias.\\
    Journal of Paediatric Orthopaedics 2004.
\item Belthur M. and Bradish C.F.\\
Late orthopaedic sequelae  following  meningococcal  septicaemia, a multicentre study..\\
Journal of Bone and Joint Surgery  Feb 2005; 87-B:236-40..
\item Bradish C.F.\\
The use of the Compass Elbow hinge for deformities in children.\\
Journal of Paediatric Orthopaedics 2004.
\item I. McMurtry, G. C. Bennet, and C. Bradish\\
      Osteotomy for congenital elevation of the scapula (Sprengel's deformity)\\
   Journal of Bone and Joint Surgery (Br), Jul 2005; 87-B: 986 - 989. 
\item Bradish C.F.\\
      Cosmetic bilateral leg lengthening. Further opinion.\\
   J Bone Joint Surgery 2006, 87-B e publication
 \item Bradish C.F., Higgins G.A.\\
Success and  application  of Taylor spatial frames  for  paediatric lower  limb lengthening and angular correction.\\
Journal of Bone and Joint Surgery, British Volume 90.SUPP III (2008): 570-570.
\item Park D.H., Bradish C.F.\\
The management  of the orthopaedic sequelae of meningococcal septicaemia patients treated to skeletal maturity\\
Journal of Bone and Joint Surgery, British Volume 93.7 (2011): 984-989
\item Park D.H., Bradish C.F.\\
An intraoperative method of calculating the mounting parameters for the Taylor Spatial Frame using the image intensifier\\
Annals of The Royal College of Surgeons of England 93.3 (2011): 260.
\item Parker L, Bradish C.F.\\
Distal tibial reconstruction in children\\
Journal of Bone and Joint Surgery, British Volume 94.SUPP XXXV (2012): 11-11.
\item C.F. Bradish. Invited chapters on Limb lengthening and Congenital Pseudarthrosis.\\
European Surgical Orthopaedics and Traumatology. Published 2014 by Springer. 
\end{enumerate}
\subsubsection{Other Publications}
\begin{enumerate}
\item Bradish C.F.\\
The carpal tunnel syndrome in patients on haemodialysis.\\
Journal of Bone and Joint Surgery (Br) 1985; 67-B: 131-132.
\item Bradish C.F., Kemp H.B., Scales J.T., Wilson J.N.\\
Distal femoral replacement using custom made endoprostheses,\\
a survivorship analysis and clinical follow up.
Journal of Bone and Joint Surgery (Br) 1987; 69-B: 276-284.
\item Bradish C.F., Lloyd G.J., Aldam C., Albert J.\\
Do non-organic signs help to predict return to activity following low back injury?\\
Spine 1988.
\item G. Coakley, C. Mathews, M. Field, A. Jones, G. Kingsley, D. Walker, M. Phillips, C. Bradish, A. McLachlan, R. Mohammed, and V. Weston on behalf of the British Society for Rheumatology Standards, Guidelines and Audit Working Group\\
BSR \& BHPR, BOA, RCGP and BSAC guidelines for management of the hot swollen joint in adults\\
Rheumatology, August 2006; 45: 1039 - 1041.
\end{enumerate}

\end{resume}
\end{document}




